A Technique for Inter-Catalogue Recommendations

### 2014-06-11 paper2/paper.tex
Edits to Experiment section

\section*{Experiment}
Our goal is to develop methods for connecting initially disconnected
recommendation graphs. Given two online retailers, each with a website
displaying their items along with several other {\em recommended} items from
their catalogue, we are presented with two disconnected recommendation graphs.
We would like to associate ``good'' recommendations for items in one catalogue
with items in the other catalogue. In this way, we are effectively introducing
edges that connect the two recommendation graphs. Formulating this
inter-retailer recommendations problem in terms of graphs offers insight in how
to evaluate our recommendation choices as well as how to choose ``good''
recommendations.  Leveraging the graph structure for evaluation is discussed in
this section while exploiting the graph for the purpose of making better
recommendations is addressed in a subsequent section.

To evaluate our inter-retailer recommendation methods, we simulate the problem
by randomly partitioning Macy's products into two disjoint sets. Given the
original recommendation graph, each partition therefore corresponds to a graph
cut. The edges in this graph cut form a {\em gold-standard} since it is assumed
that these are indeed ``good'' recommendations. Our premise is that an ideal
recommendation method could guess these gold-standard edges with high precision
and recall.

For each experiment, we choose a particular category from the Macy's catalogue
(e.g. Women Activewear, Men Dress Shirts, etc.). Since most recommendations are
between items in a common category, very few, though some, edges are lost by
confining ourselves to an individual category. Edges that are lost in this way
do not participate in the experiment and are not considered during evaluation.
Also, we randomly partition the items in the category such that all items
associated with a particular brand are entirely within a single partition. In
this way, we preclude the easiest method of associating two items: recognizing
a common brand. This is done to increase the difficulty and realism of the
experiments.

Having partitioned the graph of items, we now predict recommendation relations
between items across the partitions. Each prediction algorithm has knowledge of
all items in each partition, including their descriptions and all
recommendations (i.e.  edges) between items in a common partition. In addition,
the algorithms may exploit the fact that most items listed at www.macys.com are
accompanied by four recommended items. The algorithms do not have knowledge of
the recommendations (i.e. edges) between items across partitions. Each
prediction algorithm is then free to choose an arbitrary number of edges as long
as 1) the items connected by the predicted edge are not in the same partition
and 2) at most one edge is predicted for a particular pair of items.

>>>>

\section*{Experiment}
Our goal is to develop methods for connecting initially disconnected
recommendation graphs. Given two online retailers, each with a website
displaying their items along with several other {\em recommended} items from
their catalogue, we are presented with two disconnected recommendation graphs.
We would like to associate ``good'' recommendations for items in one catalogue
with items in the other catalogue. In this way, we are effectively introducing
edges that connect the two recommendation graphs. Formulating the inter-retailer
recommendation problem in terms of graphs offers insight on how to evaluate our
recommendation choices as well as how to choose ``good'' recommendations.
Leveraging the graph structure for evaluation is discussed in this section while
exploiting the graph for the purpose of making better recommendations is
addressed in a subsequent section, Recommender Algorithms.

To evaluate our inter-retailer recommendation algorithms, we simulate the
problem by randomly partitioning Macy's products into two disjoint sets. Given
the original recommendation graph, each partition therefore corresponds to a
graph cut. The edges in this graph cut form a {\em gold-standard} since it is
assumed that these are indeed ``good'' recommendations. Our premise is that an
ideal recommendation method could guess these gold-standard edges with high
precision and recall.

For each experiment, we choose a particular category from the Macy's catalogue
(e.g. Women Activewear, Men Dress Shirts, etc.). Since most recommendations are
between items in a common category, very few edges are lost by confining
ourselves to an individual category. Edges that are lost in this way do not
participate in the experiment and are not considered during evaluation.  Also,
we randomly partition the items in the category such that all items associated
with a particular brand are entirely within a single partition. In this way, we
preclude the easiest method of associating two items: recognizing a common
brand. This is done to increase the difficulty and realism of the experiment.

Having partitioned the graph of items, we now predict recommendation relations
between items across the partitions. Each prediction algorithm has knowledge of
all items in each partition, including their descriptions and all
recommendations (i.e.  edges) within a common partition. In addition,
the algorithms may exploit the fact that most items listed at www.macys.com are
accompanied by four recommended items. The algorithms do not have knowledge of
the recommendations (i.e. edges) between items across partitions. Each
prediction algorithm is then free to choose an arbitrary number of edges as long
as 1) the items connected by the predicted edge are not in the same partition
and 2) at most one edge is predicted for a particular pair of items.
